Comparing the Jacobi Method and LLL lattice reduction algorithms for cryptographic applications

### 2014-11-10 report/paper.tex
Known issue: code runs forever with doubles

\documentclass[11pt]{article}

\title{Comparing the Fast Jacobi Method and LLL for cryptographic applications}
\date{Fall 2014}
\author{Frederic Jacobs\\ EPFL}

@@

>>>>

\documentclass[12pt]{article}
\title{Comparing the Jacobi Method and LLL lattice reduction algorithms for cryptographic applications}
\date{Fall 2014}
\author{Frederic Jacobs\\ EPFL Bachelor Semester Project\\ frederic.jacobs@epfl.ch}

@@

\begin{abstract}
In this \cite{originalJacobiMethodLatticeBasisReduction}
\end{abstract}

\section{Introduction}

\subsection{Results and Contributions}

We show the following main results:
\begin{itemize}
\item An analysis of running times depending on factors
\end{itemize}

\subsection{Related Work}

\section{Preliminaries}

\section{Our Fast Jacobi Method Implementation}

\section{Conclusions}

\bibliographystyle{alpha}
\bibliography{references}

\section{Credits}
